\documentclass[12pt, fullpage,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\title{CS6630 Visualization Fall 2017 Project \\ Feedback exercise}
\author{Yanqing Peng, Yuwei Wang}
\begin{document}
\maketitle

In the peer feedback session, we met with the team of \textbf{Zhuoyue Zhao} and \textbf{Ya Gao}.
Their feedbacks include the following points:

\begin{enumerate}
    \item It seems that the data collection process can take a lot of time. Maybe the project should
        focus on a small time range, e.g., data since World War II.
    \item It's strange to use ``Add'' button to select countries. Using mouse click to select/unselect
        countries is more straight-forward.
    \item For the aggregation view, when a user selects a large set of countries, using line chart
        to represent countries may be hard to distinguish between countries.
    \item Colors and animations are not considered.
\end{enumerate}

We appreciate the concerns and suggestions they pointed out. We would like to answer and address
them in the following ways, respectively:
\begin{enumerate}
    \item The data collection work is indeed time-consuming. We decide to first implement the features
        on a small dataset, then extend the dataset if we have time. The extended dataset should be processed
        into the same format as the small dataset, so that it can fit the system without modifying any code.
    \item We think this suggestion is reasonable. We decide to adopt it.
    \item We plan to add multiple visualization views in aggregation panel. Users can choose
        an appropriate visualization that efficiently visualize the results.
    \item We plan to use color to highlight the selected country. Plus, if we implement the heat map
        feature, the saturation of color will be the channel. Animation can be used to show the change
        of country borders.
\end{enumerate}

We thank Zhuoyue and Ya for their useful comments.

\end{document}
